On the application of microwave acoustic resonant viral inactivation \thanks{I would be delighted to include any criticisms or comments anyone may have; preferably leave them on the GitHub issues page, or email therobotist@gmail.com, @0xDBFB7 on Twitter, or irc.0xDBFB7.com:6667 \#covid.}

### 2020-08-31 documents/paper.tex
Plate reader
Phage run 1

We've got a thing 
that's called 
Radar Love
We've got a wave
in the air

The phased-array techdemo.

@@

@@

There are a substantial number of papers in the literature which show positive effect sizes; these are listed in the bibliography. \\

@@

>>>>

@@

\begin{figure}[H]
	\makebox[\textwidth][c]{
		\includegraphics[width=\textwidth*2]{chunk_4_line_2_1.png}
	}%
	\caption{Chunk 4, it.is Founda}
\end{figure}

\begin{figure}[H]
	\captionsetup{singlelinecheck = false, justification=justified}
	\centering
	\includegraphics[width=\textwidth]{chunk_4}
	\caption{
		\light{
		\\
		We've got a thing\\
		that's called\\
		{\it Radar Love}\\}
		We've got a wave\\
		in the air}
\end{figure}

@@

There are a substantial number of papers in the literature which show positive effect sizes; a select few of these are listed in the bibliography. \\

@@

Applying microwave power to the body is already used extensively in diathermy (the internal heating of tissue for therapeutic effect) and hyperthermy (the overheating or cauterization of tissue for destructive effect). While most diathermy systems use much lower frequencies for deeper penetration, several papers have explored the 10 GHz band.

Fat and

The penetration of microwave power is very sensitive to
